\section{Introduction}

The goal of this paper is to examine metadata from medical-related smart home devices to evaluate the vulnerabilities of Internet of Things (IoT) systems. Recent research into the security of IoT systems has revealed significant vulnerabilities that adversaries with passive network capabilities could exploit. Even when data transmitted from smart devices to home routers is encrypted, they can scrutinize metadata to obtain second order information about a user. As IoT systems expand from the home into enterprise and specialized fields, the importance of confidentiality and integrity increases. One of the most sensitive applications of IoT systems is the medical field, where patient data is extremely valuable information and needs to be closely kept in accordance with the Health Insurance Portability and Accountability Act of 1996 (HIPAA) to protect patient privacy. However, many recent innovations in medical smart home devices enable users to track their personal health using smartphones, but have the potential to leak sensitive heath information. Because of the heightened consequences of adversarial behavior in the medical field, this research focuses specifically on metadata generated from smart medical IoT devices.

\subsection{IoT Devices Studied}
The data and metadata for this project was generated from a suite of medical IoT devices currently sold on the market, including the Withings Smart Blood Pressure Monitor, Withings Smart Scale, iHealth Smart Gluco-Monitoring System, iHealth Ease Wireless Blood Pressure Monitor, and 1byOne Digital Smart Wireless Scale. These Wi-Fi or Bluetooth enabled devices are connected to a router access point or directly to a smartphone, which in turn is connected to the access point. In order to intercept traffic from the IoT devices, we configured a Raspberry Pi to serve as an access point and subsequently analyzed the traffic by classifying the streams by device, protocol, and encryption. 

\subsection{Protecting digital health information}
Though the smart medical devices we examined are intended for consumer home use, similar mIoT devices are increasingly being deployed in hospital environments and medical facilities to leverage systematic data collection and easily integrate readings and measurements into electronic health records. In these realms, mIoT devices are covered by the Security and Privacy rules of the HIPAA, which dictates core standards to protect sensitive patient information. According to a summary provided by the U.S. Department of Health and Human Services, the Security Rule Requires covered entities to maintain and appropriate administrative, technical, and physical safeguards for protecting electronic patient health information (e-PHI).$^6$ Specifically, covered entities must:

\begin{enumerate}
  \item Ensure the confidentiality, integrity, and availability of all e-PHI they create, receive, maintain, or transmit;
  \item Identify and protect against reasonably anticipated threats to the security or integrity of the information;
  \item Protect against reasonably anticipated, impermissible uses or disclosures; and
  \item Ensure compliance by their workforce. 
\end{enumerate}

Additionally, the Privacy Rule protects all individually identifiable health information held or transmitted by a covered entity or its business associate, in any form or media, whether electronic, paper or oral.$^7$ The Privacy Rule calls this information protected health information (PHI). Individually identifiable health information is information, including demographic data, that relates to:

\begin{enumerate}
  \item the individual's past, present or future physical or mental health or condition,
  \item the provision of health care to the individual, or
  \item the past, present, or future payment for the provision of health care to the individual.
\end{enumerate}

Individually identifiable health information includes many common identifiers (e.g., name, address, birth date, Social Security Number).

This paper examines whether in the course of regular behavior, smart medical devices properly protect all individually identifiable health information as dictated by HIPAA. While the name of the user or patient may be protected, network observers and adversaries can see traffic being generated from each IP address. In an age where users are inseparable from their phones, an IP address is just as much a personal identifier as a social security number. By examining network traffic from an access point, it is possible to isolate traffic originating from a fixed set of IP addresses and subsequently mine the associated metadata for sensitive medical information. 

\input{body}

\section{Discussion}

These results reveal multiple known vulnerabilities within IoT devices, but there are heightened implications due to the sensitive nature of the medical metadata being disclosed. Particularly if used by healthcare professionals to measure patient vital signs/data over time, these medical IoT devices need to be more carefully examined by regulators and physician networks to increase the awareness of this information leakage before they are implemented on a wider scale. 

Additionally, the sheer diversity of devices, protocols, and lack of standardization between device manufacturers makes it very difficult to detect all vulnerabilities, or to even identify all of the devices that are connected to a network.

This research suggests that medical IoT device manufacturers are not necessarily aligned with policies including the Privacy and Security rules of HIPAA, and they may inadvertently reveal sensitive data and metadata about a user's behavior and medical condition. For example, the Privacy rule dictates that manufacturers and medical professionals protect personally identifying information such as the individual's past, present or future physical or mental health or condition. Though we found no instances of full names or biologically identifiable information being leaked, in the digital age, policy makers and manufacturers should recognize the increasingly identifiable nature of IP addresses. With users carrying smartphones in their pockets 24 hours a day, completing transactions, querying the Internet, and communicating with friends, an IP address is perhaps more individually identifiable than a social security number.

Lastly, this research underscores the lack of awareness among the general public when it comes to the confidentiality and integrity of their personal data. As technology becomes increasingly capable and complex, it will only become more difficult for users of connected devices to comprehend what sort of data can be extracted from their digital footprint, even if the devices they are using encrypt first order information. Tools like the user interface presented in this paper are in the public interest to increase the visibility of device vulnerabilities, awareness of personal confidentiality weaknesses, and accountability among device manufacturers.


\section{Conclusion}


\appendix

\section*{Acknowledgements}
Thanks to Nick Feamster, Noah Apthorpe, Dillon Reisman, Rohan Doshi, and Gudrun Jonsdottir for their thoughts and contributions to the discussions that focused this work. 
